aircraft-flask

### 2024-08-26 examples/aircore.Rmd
revise airocore

```{r obs_plot_vertt, fig.width=7, fig.height=5, eval = F}
x <- df3
x$ch4 <- x$value*1e+9obs_plot(x, 
         time = "ch4", 
         y = "altitude_final", 
         colu = "month", n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
```

>>>>

```{r obs_plot_vertt, fig.width=7, fig.height=5, eval = F}
x <- df3
x$ch4 <- x$value*1e+9
obs_plot(x, 
         time = "ch4", 
         y = "altitude_final", 
         colu = "month", n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
```

### 2024-08-26 examples/aircraft-flask.Rmd
revise airocore

obs <- "/media/sergio/ext5/obspack/obspack_ch4_1_GLOBALVIEWplus_v6.0_2023-12-01/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

Now we read the aircraft-pfp using the function `obs_read_nc`. To this date,
`solar_time` is not included for aircraft, so we `FALSE` that argument.

@@

df <- df[altitude_final < max_altitude &
           latitude < north &
           latitude > south &
           longitude < east &
           longitude > west]
dim(df)
```

@@

>>>>

obs <- "Z:/torf/obspack_ch4_1_GLOBALVIEWplus_v5.1_2023-03-08/data/nc/"
index <- obs_summary(obs = obs, 
                     categories = cate)
```

Now we read the `aircraft-flask` using the function `obs_read_nc`. To this date,
`solar_time` is not included for aircraft, so we `FALSE` that argument.

@@

# df <- df[altitude_final < max_altitude &
#            latitude < north &
#            latitude > south &
#            longitude < east &
#            longitude > west]
dim(df)
```

@@

```{r vertplot, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
x <- df3
x$ch4 <- x$value*1e+9
png("../man/figures/obsplot_aircraftflask_vert.png", width = 1500, height = 1000, res = 200)
obs_plot(x, 
         time = "ch4", 
         y = "altitude_final", 
         colu = "month", n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
dev.off()
```

```{r obs_plot_vertt, fig.width=7, fig.height=5, eval = F}
x <- df3
x$ch4 <- x$value*1e+9
obs_plot(x, 
         time = "ch4", 
         y = "altitude_final", 
         colu = "month", n = c(1L, 3L, 6L, 8L, 9L, 11L, 12L), 
         type = "b", 
         xlab = expression(CH[4]~ppb), 
         ylab = "altitude (m)")
```

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_aircraftflask_vert.png?raw=true)
